NaN gates and flip FLOPS

### 2019-02-24 nand/paper.tex
Abrupt power failures are a good reminder to back up your work

% ok the STM32f3 is supported, has FPU, 51 IO pins,
% here is an example breakout:
% http://ebrombaugh.studionebula.com/embedded/stm32f303breakout/index.html
% requires a crystal, voltage regulator, and some filter capacitors,
% but looks manageable. (And the chip has some 5V tolerant TTL I/O
% pins too, which could be nice for other projects)
% also maybe a ferrite bead (for input to analog VDDA, so probably
% not needed for this project)

@@

let x = nand(a0, a2)   // !a0 || !a2
let y = nand(b0, b2)   // !b0 || !b2

let out =

>>>>

% ok the STM32f3 is supported, has FPU, 51 IO pins,
% specifically like the
% https://www.mouser.com/ProductDetail/STMicroelectronics/STM32F303RDT7?qs=%2Fha2pyFaduikpRt0bOqlahEvgTujL2BrdYPen6RZRRk%3D

% here is an example breakout:
% http://ebrombaugh.studionebula.com/embedded/stm32f303breakout/index.html
% requires a crystal, voltage regulator, and some filter capacitors,
% but looks manageable. (And the chip has some 5V tolerant TTL I/O
% pins too, which could be nice for other projects)
% also maybe a ferrite bead (for input to analog VDDA, so probably
% not needed for this project)

@@

let x = nand(!a0, !a2)
let y = nand(!b0, !b2)
let z = nand(a1, b1)

let w = Not(Nand(Not(x), Not(y)))
let out = Not(Nand(w, Not(z))

... this is pretty much a straightforward Nand construction.
I guess it doesn't really simplify much across units.

or with more gates,
Not(Or(z, Or(y, x)))

and I mean obviously it's just
And(Not (Or (a0, a2, b0, b2)), a1, b1)
if you have all the gates directly.

we can certainly make chips implementing each of these gates,
since we have floating point implementations of each, but
then we sort of lose the final joke since we'd just build
a floating point unit that computes the NAND instruction.

so let's try the pure-nand approach.

implementing the nots also with nands, this works out to 14
gates, which is ``just'' three chips. very reasonable. I was
actually hoping for it to be a little more ridiculous.
(maybe there is a lower pin-count device with an easier
package? programming them is still going to be a huge pain)

if we used the meta-nand gates, we'd have 14 * 3 = 42 chips,
which is OTOH probably too many.

with this meta-fpu, we have 2 binary3 inputs and 1 binary3
output, but each ``bit'' is represented as a binary3 number
itself. So this makes (3 * 2 + 1) * 3 = 27 wires to interface
with it. This is exactly as many GPIO the pi has, so that
is good, although IIRC a few pi pins have special annoyances,
and it doesn't leave us any space for a programmer.
Maybe just best to make a separate programmer and connect it
up to different test points manually. Then we could reuse
the programmer pretty easily.

Note that in a pinch we can ``cheat'' pretty easily here
since some of the pins have constant values. Probably justifiable
is that the meta-nand always outputs 0 (nan) for g and 1 (inf) for h,
plus two of the bits of i are fixed because it will only represent
nan or inf. But really would be ``prettiest'' to not make this cheat,
I mean, it's a pretty silly excursion anyway.

oh jk there is actually gpio0 too, so 28 pins on pi.
